Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2018-10-27 pkg/disttree/inst/draft/draft.Rnw
small corrections in references and revisions based on Torsten's feedback
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2366 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 0015264e7bafac16500e253e54cd5a13dad363e6

\subsubsection*{Variable Selection}
\hlc{Generally, there are many possibilities how to specify the variables that are
to be included in a model. Especially for a low number of variables all types
of interactions can be employed and mixed effect models and separations into 
main effects and interaction effects can be considered allowing for easier 
interpretations} (see for example \cite{Wood+Scheipl+Faraway:2013}, 
\cite{Goicoa+Adin+Ugarte:2018}, \cite{Ugarte+Adin+Goicoa:2017}).
\hlc{However, in the application presented in} Section~\ref{sec:precipitation}
\hlc{altogether 80 variables are available. Even if only paired interactions were
considered this would already lead to 3160 additional covariates in the model
making it very difficult to keep the model manageable regarding computational
costs but also interpretability. Therefore, only main effects are considered
for the distributional forest and the boosted GAMLSS which both automatically
select covariates while meteorological expert knowledge was applied to 
select covariates and specify interactions for the prespecified GAMLSS.

@@

\hlc{Alternatively, a distribution including an additional parameter capturing 
skewness could be applied} \citep{Scheuerer+Hamill:2015, Baran+Nemoda:2016}. 
\hlc{For example, in transformation forests} \citep{Hothorn+Zeileis:2017} 
\hlc{a very flexible five-parametric distribution family is employed such 
that skewness can be modeled explicitly.
Evaluating further distributions might be of interest but this would go beyond the
scope of this manuscript.
}

@@

>>>>

\subsubsection*{Variable Selection}
\hlc{Generally, there are many possibilities how to specify the variables that are
to be included in a model. Especially for a low number of variables all types
of interactions can be employed and mixed effect models and separations into 
main effects and interaction effects can be considered allowing for easier 
interpretations} (see for example \cite{Wood+Scheipl+Faraway:2013}, 
\cite{Goicoa+Adin+Ugarte:2018}, \cite{Ugarte+Adin+Goicoa:2017}).
\hlc{However, in the application presented in} Section~\ref{sec:precipitation}
\hlc{altogether 80 variables are available. Even if only paired interactions were
considered this would already lead to 3160 additional covariates in the model
making it very difficult to keep the model manageable regarding computational
costs but also interpretability. 
Therefore, only additive effects are considered for the boosted GAMLSS which
automatically selects covariates while meteorological expert knowledge was 
applied to select covariates and specify interactions for the prespecified 
GAMLSS. For the distributional forest no prespecification is required as it
automatically selects covariates and also detects interaction effects.

@@

\hlc{Alternatively, a distribution including an additional parameter capturing 
skewness could be applied} \citep{Scheuerer+Hamill:2015, Baran+Nemoda:2016}. 
\hlc{For example, in transformation forests} \citep{Hothorn+Zeileis:2017} 
\hlc{a very flexible parametric distribution characterised by the transformation 
function is employed such that higher moments can be modeled implicitly.
Evaluating further distributions might be of interest but this would go beyond the
scope of this manuscript.}

@@

%\begin{supplement}[id=supp1]
%  \sname{Supplement 1}
%  \stitle{Different Response Distributions}
%  \slink[doi]{10.1214/00-AOASXXXXSUPP}
%  \sdatatype{.pdf}" 
%  \sdescription{
%  In the case study presented in the main manuscript ``Distributional Regression
%  Forests for Probabilistic Precipitation Forecasting in Complex Terrain''
%  the novel distributional regression forests are based on a Gaussian response distribution,
%  left-censored at zero to accomodate both the non-negativity of precipitation and
%  the point mass at zero. To assess the goodness of fit of this response distribution
%  this supplement employs the same evaluations as in the main manuscript but based on
%  two other distributional assumptions: A logistic distribution, left-censored at zero,
%  is employed to potentially better capture heavy tails -- and a two-part hurdle model
%  combining a binary model for zero vs.\ positive precipitation and a Gaussian model,
%  truncated at zero, for the positive precipitation observations. The latter could
%  potentially better discriminate determinants of the occurrence of precipitation
%  vs.\ the amount of precipitation given that it occurs.
%}
%\end{supplement}

%\begin{supplement}[id=supp2]
%  \sname{Supplement 2}
%  \stitle{Stationwise Evaluation}
%  \slink[doi]{10.1214/00-AOASXXXXSUPP}
%  \sdatatype{.pdf}" 
%  \sdescription{
%  In the case study presented in the main manuscript ``Distributional Regression
%  Forests for Probabilistic Precipitation Forecasting in Complex Terrain''
%  the novel distributional regression forests are evaluated and compared with
%  other distributional regression approaches on 95 meteorological stations.
%  Moreover, further details -- including a cross-validation analysis -- are
%  preformed for only one station, Axams. To show that Axams is a fairly typical
%  station and similar insights can be obtained for other stations as well,
%  this supplements presents the same analysis as in Section~3.3 of the main
%  manuscript for 14~further meteorological stations.
%}
%\end{supplement}
